---
title: "CSV to point"
output: html_document
---


# Clear workspace

```{r}
rm(list=ls()) 
```

# Overview

Create spatial points data  fram  for plots that burned from 2001 to present. Point data will be used  to extract  dnbr and RdNBR values from satellite imagery of of burn severity  calculations.

# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(ggplot2)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(latticeExtra)
library(sf)
```




# Data

## CSV

```{r}
df = read.csv("../data/recovery_study_ts_segments.csv")
```

```{r}
head(df)
```
```{r}
str(df)
```

```{r}
unique(df$startYear)
```

## States
```{r}
states= st_read("../data/states-shapefile/s_11au16.shp", "s_11au16")
```
## EPA Ecoregions
```{r}
eco= st_read("../data/us_eco_l3_state_boundaries/us_eco_l3_state_boundaries.shp", "us_eco_l3_state_boundaries")
```

# Projections
USA Contiguous Albers Equal Area Conic, USGS (EPSG = 5070 or 102003)
https://guides.library.duke.edu/r-geospatial/CRS

+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs 
```{r}
us_proj = "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
```


```{r}
st_crs(states)
```

# Filter states
```{r}
unique(states$NAME)
```

```{r}
lower48 = states %>%
  filter(!NAME %in% c('Alaska', 'American Samoa', 'Puerto Rico', "Virgin Islands", "Guam", "Northern Marianas"))

lower48
```

# Reproject
```{r}
lower48_proj <- st_transform(lower48, us_proj)
```

```{r}
eco_proj <- st_transform(eco, us_proj)
```

# Data frame to  points (spatial dataframe)

## add row number
```{r}
df1 = df %>% 
  unite("id", plotid, startYear, remove = FALSE)

df1
```
```{r eval=FALSE, include=FALSE}
write.csv(df1, '../outputs/csv/data-uniqueID.csv',  row.names = FALSE)
```
Define coordinates and generate spatial point data frame with attributes

```{r}
coords_df = cbind(df1$x, df1$y)
df_pt <- SpatialPointsDataFrame(coords_df, proj4string = CRS(us_proj), data = df1)
```




# Transform from sp to sf

```{r}
df_pt_sf = st_as_sf(df_pt)
```

# Join states to points
```{r}
df_states = st_join(st_make_valid(df_pt_sf), lower48_proj, largest=TRUE) 
```


```{r}
df_states1 = df_states %>% 
  dplyr::select(id, plotid:NAME, geometry) 
```

```{r}
df_states1
```

```{r eval=FALSE, include=FALSE}

plot(lower48_proj)
plot(df_states, add=TRUE)
```

## Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(df_states1, "../outputs/point_data/harvest_pt_states.shp", driver="ESRI Shapefile")
```

# Join Ecoregion to points
```{r}
df_eco = st_join(st_make_valid(df_states1), eco_proj, largest=TRUE) 
```

```{r}
df_eco 
```

## Remove geometry and write attributes to CSV
```{r eval=FALSE, include=FALSE}
df_eco %>% 
  st_set_geometry(NULL) %>% 
        write.csv(., '../outputs/csv/Points-EcoRegions.csv',  row.names = FALSE)
  
```

## Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(df_eco, "../outputs/point_data/harvest_pt_states_ecoregions.shp", driver="ESRI Shapefile")
```




# Filter by State
```{r}
or_wa = df_states1 %>% filter(NAME %in% c("Oregon", "Washington"))

or_wa
```

```{r eval=FALSE, include=FALSE}
st_write(or_wa, "../outputs/point_data/harvest_pt_OR_WA.shp", driver="ESRI Shapefile")
```

# Filter into 8 year increments

```{r}
target1 = c(1984, 1985, 1986, 1987)
```

```{r}
df_1984 = df_pt_sf %>% filter(startYear == 1984)
df_1984
```

```{r eval=FALSE, include=FALSE}
st_write(df_1984, "../outputs/point_data/harvest_pt_1984.shp", driver="ESRI Shapefile")
```