---
title: "NBR compare"
output: html_document
---

# Overview


# Packages

```{r}
library(tidyverse)
library(cowplot)
library(data.table)
```

# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```

```{r}

reg_theme = theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        legend.title = element_blank())

```

```{r}
bar_theme = theme_bw() + 
  theme(legend.position = "none", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black")) 
```

```{r}
ecoPalette <- c("#b5b35c", "#556b2f")
```

geom_point(size=1.5, shape=1, color= "grey50")  

# Data
```{r}
data = read.csv( '../data/csv/dataAllNBRYears.csv')
```

```{r}
longdata = read.csv( '../data/csv/dataAllNBRYearsLongFormData.csv')
```

```{r}
head(longdata)
```

```{r}
eco = read.csv( '../data/csv/Points-EcoRegions.csv')
```

# States for East and West

```{r}
east = c("Alabama" , "Arkansas", "Connecticut", "District of Columbia", "Delaware", "Florida", "Georgia", "Illinois", "Indiana", "Iowa" , "Kentucky",  "Louisiana", "Massachusetts", "Maine", "Michigan", "Minnesota", "Mississippi", "North Carolina", "New Hampshire", "New Jersey", "New York", "Ohio", "Pennsylvania", "Rhode Island", "Tennessee", "Virginia", "Vermont", "Wisconsin", "West Virginia",  "Missouri", "South Carolina", "Maryland")


west = c("Arizona", "California", "Colorado", "Idaho", "Kansas", "Montana", "North Dakota", "Nebraska", "New Mexico",  "Nevada", "Oklahoma", "Oregon", "South Dakota",  "Texas", "Utah", "Washington", "Wyoming")
```


# Organize
## Subset ecoregion dataframe
```{r}
eco1 = eco %>% dplyr::select(id, US_L3CODE:NA_L1NAME, EPA_REGION:L1_KEY)
eco1
```

## Subset years of interest
```{r}
df <- longdata[longdata$nbrYr==longdata$year, ]

df
```

## Reformat to wider
```{r}
df1 = df %>% dplyr::select(!nbrYr) %>%
  pivot_wider(names_from = c(prePost, startEnd), 
    values_from = c(nbr, year))

df1
```

## Add dNBR and RdNBR
```{r}

df2 = df1 %>% mutate(dnbr = nbr_preNbr_startYear-nbr_postNbr_endYear) %>%
  mutate(rdnbr_bottom = (sqrt(abs(nbr_preNbr_startYear/1000))))
df2
```
```{r}
df3 = df2 %>% mutate(rdnbr = dnbr/rdnbr_bottom) 
df3
```

```{r}
east_df = df3 %>% filter(NAME %in% east)
east_df
```

```{r}
west_df = df3 %>% filter(NAME %in% west)
west_df
```


## Add EcoRegion Data
```{r}
df4 = merge(df3, eco1, by="id")
df4
```

## Split States by East/West
# Eco Region Data
```{r}
n_distinct(df4$US_L3NAME)
n_distinct(df4$NA_L3NAME)
n_distinct(df4$US_L2NAME)
n_distinct(df4$US_L1NAME)
n_distinct(df4$EPA_REGION)
n_distinct(df4$L3_KEY)
n_distinct(df4$NA_L2CODE)
```
# Calculate proportion Misclassified by threshold


```{r}

east_thresholds = east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300))) %>%
  mutate(p_lte100 = n_lte100/n_count) %>%
  mutate(p_lte150 = n_lte150/n_count) %>%
  mutate(p_lte200 = n_lte200/n_count) %>%
  mutate(p_lte250 = n_lte250/n_count) %>%
  mutate(p_lte300 = n_lte300/n_count) 

east_thresholds
```
```{r}
write.csv(east_thresholds, '../outputs/east_thresholds.csv',  row.names = FALSE)
```

# Thresholds

# Threshold calculate Overall Accuracy

## East
```{r}
east_mult_thr = east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (675+1277)) 

east_mult_thr
```

```{r}
write.csv(east_mult_thr, '../outputs/Multiple_east_thresholds.csv',  row.names = FALSE)
```

```{r}
east_thresholds2 = east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100 & rdnbr>=500)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125 & rdnbr>=500)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150 & rdnbr>=500)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175 & rdnbr>=500)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200 & rdnbr>=500)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225 & rdnbr>=500)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250 & rdnbr>=500)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275 & rdnbr>=500)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300 & rdnbr>=500)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325 & rdnbr>=500)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350 & rdnbr>=500)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375 & rdnbr>=500))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (675+1277)) 

east_thresholds2
```

```{r}
write.csv(east_thresholds2, '../outputs/east_thresholds2.csv',  row.names = FALSE)
```
## West
```{r}

west_mult_thr = west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (190+445)) 
  
west_mult_thr
```

```{r}
write.csv(west_mult_thr, '../outputs/Multiple_west_thresholds.csv',  row.names = FALSE)
```

## East
```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  mutate(classified = changeNote)
```
# Threshold calculate Overall Accuracy

## East
```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (675+1277)) %>%
  mutate(clearcut_accuracy = clearcut/Total*100) %>%
  mutate(thinning_accuracy = thinning/Total*100)
```

## West
```{r}

west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (190+445)) %>%
  mutate(prop_clearcut = clearcut/190) %>%
  mutate(prop_thin = thinning/445)
  

```

# Threshold calculate Omission Error

## East
```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (675+1277)) %>%
  mutate(clearcut_accuracy = (675-clearcut)/Total*100) %>%
  mutate(thinning_accuracy = (1277-thinning)/Total*100)
```

## West
```{r}

west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (190+445)) %>%
  mutate(clearcut_accuracy = (190-clearcut)/Total*100) %>%
  mutate(thinning_accuracy = (445-thinning)/Total*100)
  

```

# Threshold calculate Comission Error

## East
```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
  summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (675+1277)) %>%
  mutate(clearcut_accuracy = (675-clearcut)/Total*100) %>%
  mutate(thinning_accuracy = (1277-thinning)/Total*100)
```

## West
```{r}

west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  pivot_longer(n_lte100:n_lte375, names_to = "threshold", values_to = "count") %>%
  dplyr::select(!n_count) %>%
  pivot_wider(names_from = changeNote, values_from = count) %>%
   mutate(Total = (190+445)) %>%
  mutate(clearcut_accuracy = (190-clearcut)/Total*100) %>%
  mutate(thinning_accuracy = (445-thinning)/Total*100)
  

```

# Threshold explore

```{r}

west_thresholds = west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300)),
              n_lte325 = length(which(nbr_postNbr_endYear <= 325)),
              n_lte350 = length(which(nbr_postNbr_endYear <= 350)),
              n_lte375 = length(which(nbr_postNbr_endYear <= 375))) %>%
  mutate(p_lte100 = n_lte100/n_count) %>%
  mutate(p_lte150 = n_lte150/n_count) %>%
  mutate(p_lte200 = n_lte200/n_count) %>%
  mutate(p_lte250 = n_lte250/n_count) %>%
  mutate(p_lte300 = n_lte300/n_count) 

west_thresholds
```
```{r}
write.csv(west_thresholds, '../outputs/west_thresholds.csv',  row.names = FALSE)
```

```{r}
west_thresholds2 = west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
   group_by(changeNote) %>%
    summarize(n_count = n(),
              n_lte100 = length(which(nbr_postNbr_endYear <= 100 & rdnbr>=500)),
              n_lte125 = length(which(nbr_postNbr_endYear <= 125 & rdnbr>=500)),
              n_lte150 = length(which(nbr_postNbr_endYear <= 150 & rdnbr>=500)),
              n_lte175 = length(which(nbr_postNbr_endYear <= 175 & rdnbr>=500)),
              n_lte200 = length(which(nbr_postNbr_endYear <= 200 & rdnbr>=500)),
              n_lte225 = length(which(nbr_postNbr_endYear <= 225 & rdnbr>=500)),
              n_lte250 = length(which(nbr_postNbr_endYear <= 250 & rdnbr>=500)),
              n_lte275 = length(which(nbr_postNbr_endYear <= 275 & rdnbr>=500)),
              n_lte300 = length(which(nbr_postNbr_endYear <= 300 & rdnbr>=500))) %>%
  mutate(p_lte100 = n_lte100/n_count) %>%
  mutate(p_lte125 = n_lte125/n_count) %>%
  mutate(p_lte150 = n_lte150/n_count) %>%
  mutate(p_lte175 = n_lte175/n_count) %>%
  mutate(p_lte200 = n_lte200/n_count) %>%
  mutate(p_lte225 = n_lte225/n_count) %>%
  mutate(p_lte250 = n_lte250/n_count) %>%
  mutate(p_lte175 = n_lte175/n_count) %>%
  mutate(p_lte300 = n_lte300/n_count) 

west_thresholds2
```

```{r}
write.csv(west_thresholds2, '../outputs/west_thresholds2.csv',  row.names = FALSE)
```

# Plots East
```{r}
east_df
```

## East Density plot
```{r}
east_density = east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = nbr_postNbr_endYear, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 250) +
  xlab("Post disturbance NBR") +
      ylab("Density") +
  reg_theme

east_density
```

```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = dnbr, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 250) +
  xlab("Post disturbance NBR") +
      ylab("Density") +
  reg_theme


```

```{r}
east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = rdnbr, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 250) +
  xlab("Post disturbance NBR") +
      ylab("Density") +
  reg_theme


```
## East scatter plot

```{r}
east_plot = east_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = nbr_postNbr_endYear, y =rdnbr, color = changeNote)) +
  geom_point(size=1.5, shape=1)  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 300) +
  geom_vline(xintercept = 250) +
  geom_vline(xintercept = 200) +
  xlab("Post disturbance NBR") +
      ylab("RdNBR") +
  reg_theme

east_plot
```
```{r}
west_df
```

## West Density
```{r}
west_density = west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = nbr_postNbr_endYear, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 150) +
  xlab("Post disturbance NBR") +
      ylab("Density") +
  reg_theme 

west_density
```

```{r}
west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = dnbr, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("dNBR") +
      ylab("Density") +
  reg_theme 


```

```{r}
west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = rdnbr, color = changeNote)) +
  geom_density()  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("RdNBR") +
      ylab("Density") +
  reg_theme 


```
## West Scatter
```{r}
west_plot = west_df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = nbr_postNbr_endYear, y =rdnbr, color = changeNote)) +
  geom_point(size=1.5, shape=1)  +
  scale_color_manual(values = c('#d8b365','#5ab4ac')) +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = 300) +
  geom_vline(xintercept = 250) +
  geom_vline(xintercept = 200) +
  xlab("Post disturbance NBR") +
      ylab("RdNBR") +
  reg_theme 

west_plot
```

# Combine East and West plots

## Scatter
```{r fig.height=5, fig.width=3}

fig1 = cowplot::plot_grid(east_plot, west_plot, ncol=1)
fig1
```

```{r fig.height=5, fig.width=3}

fig2 = fig1 +
  draw_label("(a)", x = 0.04, y = .99, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
   draw_label("(b)", x = 0.04, y = .49, fontfamily = "sans", fontface = "bold", color = "black", size = 10) 
  
fig2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/East-West-Thresholds.png", plot = fig2, width = 3, height = 5, units = c("in"), dpi = 600)
```

## Density


```{r fig.height=5, fig.width=3}

density_fig1 = cowplot::plot_grid(east_density, west_density, ncol=1)
density_fig1
```

```{r fig.height=5, fig.width=3}

density_fig2 = density_fig1 +
  draw_label("(a)", x = 0.04, y = .99, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
   draw_label("(b)", x = 0.04, y = .49, fontfamily = "sans", fontface = "bold", color = "black", size = 10) 
  
density_fig2
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/East-West-Density.png", plot = density_fig2, width = 3, height = 5, units = c("in"), dpi = 600)
```

# Plots

```{r}
p1 = df %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = nbrYr, y = nbr, color = startEnd)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~changeNote) 

p1

```


```{r}
ggsave("../figures/ClearCutThinStartEndNBR.png", plot=p1 ,  dpi = 600)
```
```{r}
df4
```

```{r}
df4 %>% 
  filter(changeNote == "clearcut") 
```

```{r}
df4 %>% 
  filter(changeNote == "thinning") 
```

```{r}
p2 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=EPA_REGION)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~changeNote) 

p2
```



```{r}
p3 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=as.factor(NA_L2CODE))) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~changeNote) 

p3
```



```{r}
p4 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=as.factor(NA_L1CODE))) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~changeNote) 

p4
```

```{r}
p5 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=changeNote)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~as.factor(NA_L1CODE)) 

p5
```
```{r}
ggsave("../figures/ClearCutThinEco1rdnbr.png", plot=p5 ,  dpi = 600)
```

```{r}
p6 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = dnbr, color=changeNote)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~as.factor(NA_L1CODE)) 

p6
```
```{r}
ggsave("../figures/ClearCutThinEco1dnbr.png", plot=p6 ,  dpi = 600)
```

```{r}
df4
```
```{r}
p7 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(.,  aes(x = year_postNbr_endYear, y = nbr_postNbr_endYear, color=changeNote)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~as.factor(NA_L1CODE)) 

p7
```
```{r}
ggsave("../figures/ClearCutThinEco1Postnbr.png", plot=p7 ,  dpi = 600)
```

```{r}
p8 = df4 %>% 
  filter(changeNote %in% c("clearcut", "thinning")) %>%
  ggplot(., aes(x = year_preNbr_startYear, y = nbr_preNbr_startYear, color=changeNote)) +
  geom_point() +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~as.factor(NA_L1CODE)) 

p8
```


# Plots with added LC1 end and LC2 end
```{r}
target_startLC1 = c("Trees")
target_startLC2 = c("trees")
target_endLC1 = c( "Grass/forb/herb", "Barren", "Shrubs")
target_endLC2 = c( "grassForbHerb", "grassForbHerb|naturalBarren", "shrubs", "naturalBarren" )

```


```{r}
p9 = df4 %>% 
  filter(NA_L1CODE ==8) %>%
  filter(startLC1 %in% target_startLC1)  %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 8") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p9
``` 
```{r}
ggsave("../figures/EcoReg8EndLC12RdNBR.png", plot=p9 ,  dpi = 600)
```

```{r}
p10 = df4 %>% 
  filter(NA_L1CODE ==5) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 5") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p10
``` 

```{r}
ggsave("../figures/EcoReg5EndLC12RdNBR.png", plot=p10 ,  dpi = 600)
```

```{r}
p11 = df4 %>% 
  filter(NA_L1CODE ==6) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 6") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p11
``` 

```{r}
ggsave("../figures/EcoReg6EndLC12RdNBR.png", plot=p11 ,  dpi = 600)
```

```{r}
p12 = df4 %>% 
  filter(NA_L1CODE ==7) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = rdnbr, color=changeNote)) +
  geom_point() +
  ggtitle("Ecoregion 7") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p12
``` 

```{r}
ggsave("../figures/EcoReg7EndLC12RdNBR.png", plot=p12 ,  dpi = 600)
```


```{r}
p13 = df4 %>% 
  filter(NA_L1CODE ==8) %>%
  filter(startLC1 %in% target_startLC1)  %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = dnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 8") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p13
``` 
```{r}
ggsave("../figures/EcoReg8EndLC12dNBR.png", plot=p13 ,  dpi = 600)
```

```{r}
p14 = df4 %>% 
  filter(NA_L1CODE ==5) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = dnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 5") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p14
``` 

```{r}
ggsave("../figures/EcoReg5EndLC12dNBR.png", plot=p14 ,  dpi = 600)
```

```{r}
p15 = df4 %>% 
  filter(NA_L1CODE ==6) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = dnbr, color=changeNote)) +
  geom_point() +
   ggtitle("Ecoregion 6") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p15
``` 

```{r}
ggsave("../figures/EcoReg6EndLC12dNBR.png", plot=p15 ,  dpi = 600)
```

```{r}
p16 = df4 %>% 
  filter(NA_L1CODE ==7) %>%
  filter(endLC1 %in% target_endLC1 | endLC2 %in% target_endLC2) %>%
  ggplot(., aes(x = year_postNbr_endYear, y = dnbr, color=changeNote)) +
  geom_point() +
  ggtitle("Ecoregion 7") +
  theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
         plot.title = element_text(size=10))
  
p16
``` 

```{r}
ggsave("../figures/EcoReg7EndLC12dNBR.png", plot=p16 ,  dpi = 600)
```