---
title: "Small Raster organize for lm"
output: html_document
---
# Overview
This script takes the 3000 point subset that was shared with Tony Ives for an initial test in PARTs and applies a linear regression to each recovery trajectory. 

The 3000 points are a subset from ~500,000 pixels for an initial test area in the Oregon Coast Range near Roseburg. This test set was created with an arbitrary post-disturbance NBR threshold.

# Packages
```{r message=FALSE, warning=FALSE}

library(ggplot2)
library(tidyverse)
library(broom)
library(sp) # spatial data
library(rgdal) # geospatial data
library(rgeos) # GIS Geometry
library(sf)
```


```{r}
df = read.csv('../data/csv/OR3000.csv')

```

```{r}
head(df)

```
```{r}
df1 = df %>% dplyr::select(year1:harvestYr) %>%
  rename("1"=year1, "2"=year2, "3"=year3, "4"=year4, "5"=year5, "6"=year6) %>%
  mutate(location = row_number()) %>%
  pivot_longer(
    cols = 1:6,
    names_to = "recoveryYr",
    values_to = "nbr",
    values_drop_na = TRUE
  )

df1
```

```{r}
df1
```
```{r}
model = df1 %>%
  dplyr::select(location:nbr) %>%
  nest(data=-location) %>%                             
  mutate(reg = purrr::map(data, ~lm(nbr~recoveryYr, .))) %>%   # do the regression
  mutate(intercept=map_dbl(reg, ~coefficients(.)[1]),         # get values form regression
         slope=map_dbl(reg, ~coefficients(.)[2]))

model
```

```{r}
model2 = model %>% mutate(intercept = round(intercept ,digit=2)) %>% mutate(slope = round(slope,digit=2)) %>% filter(slope <0)


model2
```

```{r}

model3 = merge(model2, df1, by="location") %>% filter(recoveryYr=="1") %>% dplyr::select(location, intercept:nbr)

model3
```


# Other code


```{r}
locations<-c("a","b","c")

proportion.I<-c(0.073846154, 0.079710145, 0.063218391)

proportion.II<-c(0.049773659, 0.033756955, 0.011237956)

proportion.III<-c(0.090322581, 0.100917431, 0.08051443)

abundance.I<-c(331,331,331)

abundance.II<-c(178,178,178)

abundance.III<-c(87,87,87)

output.slope<-c(5.539e-05, -4.665e-05, -2.819e-05)

output.intercept<-c(5.128e-02, 8.073e-02, 5.726e-02)

df<-data.frame(locations, proportion.I, proportion.II, proportion.III, abundance.I, abundance.II, abundance.III, output.slope, output.intercept)
```

```{r}
df
```

```{r}
df %>% 
  select(-starts_with("output")) %>%                   #drop "answers"
  pivot_longer(proportion.I:abundance.III) %>%         # convert to long format
  separate(name, into = c("var", "idx")) %>%           # get values from column names
  pivot_wider(names_from=var, values_from=value) %>%   # go back to wide
  nest(data=-locations) %>%                             
  mutate(reg = map(data, ~lm(abundance~proportion, .))) %>%   # do the regression
  mutate(intercept=map_dbl(reg, ~coefficients(.)[1]),         # get values form regression
         slope=map_dbl(reg, ~coefficients(.)[2]))

```

`

# Projections
USA Contiguous Albers Equal Area Conic, USGS (EPSG = 5070 or 102003)
https://guides.library.duke.edu/r-geospatial/CRS

+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs 
```{r}
us_proj = "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
```

```{r}
wgs_proj = "+proj=longlat +datum=WGS84 +no_defs"
```

# Covert to points
```{r}
coords_df = cbind(model3$lng, model3$lat)
model3_pt <- SpatialPointsDataFrame(coords_df, proj4string = CRS(wgs_proj), data = model3)
```


# Transform from sp to sf

```{r}
model3_pt_sf = st_as_sf(model3_pt)
```

```{r eval=FALSE, include=FALSE}
st_write(model3_pt_sf, "../outputs/point_data/ORSmallDataNegSlope.shp", driver="ESRI Shapefile")
```